Staged Abstract Interpreters

### 2019-09-11 paper/40_absinterp.tex
polish

This monad stack scheme (@AnsM[T]@) leads to a different type of grounded
result. Recall that in the concrete setting, we only have a reader monad (for
environments) and a state monad (for stores). The reader effect is not
persistent to the final result. Hence, together with the value produced by the
interpreter, the final result type is just a pair of @Value@ and @Store@.
However, under the new monad stack for abstract interpretation, we have a
@SetT@ monad transformer inside the environment monad and store monad. Therefore, the type
@Set@ becomes the container type of the pairs of values and stores, i.e.,
@Set[(Value, Store)]@.  Also, note that the reader and state monad for the
caches both inhibit internally of the nondeterminism monad; as the result, the
final result type is paired the set of value-stores with the cache type from
that state monad, as shown below.
\begin{lstlisting}
  type Result = (R[Set[(Value, Store)]], R[Cache])
\end{lstlisting}

>>>>

This monad stack scheme (@AnsM[T]@) leads to a different type of grounded
result. Recall that in the concrete setting, we only have a reader monad (for
environments) and a state monad (for stores). The reader effect is not
persistent to the final result. Hence, together with the value produced by the
interpreter, the final result type is just a pair of @Value@ and @Store@.
However, under the new monad stack for abstract interpretation, we have a
@SetT@ monad transformer inside the environment monad and store monad. Therefore, the type
@Set@ becomes the container type of the pairs of values and stores, i.e.,
@Set[(Value, Store)]@.  Also, note that the reader and state monad for the
caches both inhibit internally of the nondeterminism monad; as the result, the
final result type pairs the set of value-stores with the cache type from
that state monad, as shown below.
\begin{lstlisting}
  type Result = (R[Set[(Value, Store)]], R[Cache])
\end{lstlisting}
